---
title: "COVID-19"
author: "Härje Widing"
date: '2021-02-06'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Features Level 1

* Gender: Female and Male

* Deaths 

* Cases

* Country

* Vaccinated


## Countries done


* Spain

* Belgium 

* Switzerland

* UK?

* Germany 

* Sweden 

## Not done 

* Denmark 

* Italy 

# https://globalhealth5050.org/ not uesd

```{r}
library(countrycode)
library(COVID19)
library(readxl)
library(httr)
library(stringr)
library(tidyr)
library(dplyr)
set_year <- function(date){
  # Saving year to date
  rDate <- c()
  y <- 2020 # Start year
  for(d in 1:length(date)){
    if(length(date) > 2){
      if(grepl('Jan',date[d]) && (grepl('Dec',date[d-1]) || grepl('Nov',date[d-1]))){
        y <- y+1
      }
    }else{
      y <- 2021
    }
    dat <- paste(date[d],y)
    rDate[d] <- dat
  }
  return(rDate)
}
clean_text <- function(str){
  ret <- c()
  for(i in str){
    t <- strsplit(i,"\\.")[[1]]
    t <- paste(t[grepl('^[A-Za-z]+$',t)], collapse = "_")
    ret <- c(ret, t)
  }
  return(ret)
}
set_date_week <- function(str,format = "d-m-y"){
  m <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun","Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
  set_m <- function(i){
    i <- strsplit(i," ")[[1]]
    i[2] <- which(m == i[2])
    return(paste(i,collapse = "-"))
  }
  str <- set_year(str)
  ret <-as.Date(unlist(lapply(str, set_m)),"%d-%m-%Y")
  if(format == "W")
    ret <- as.integer(strftime(ret,format = "%V"))
  return(ret)
}
clean_presentage <- function(str){
  ret <- c()
  str <- as.vector(str)
  for(i in str){
    if(i != ""){
      ret <- c(ret, as.numeric(strsplit(i,"%")[[1]]) / 100)
    }else{
      ret <- c(ret, NA)
    }
  }
  return(ret)
}

as.numeric.factor <- function(x) {
  if(is.factor(x)){
    x <- as.numeric(levels(x))[x]
  }
  if(is.character(x)){
    x <- as.numeric(x)
  }
  return(x)
}

covid19globalhealth <- function(country="World"){
  # Collecting gender identifing deaths from different countries
  # from https://globalhealth5050.org/
  if(country == "World"){
    url <- "https://globalhealth5050.org/?_covid-data=datasettable&_extype=csv"
    data <- read.csv2(url, sep=",")
    colnames(data) <- clean_text(colnames(data))
    data[,6] <- clean_presentage(data[,6])
    data[,7] <- clean_presentage(data[,7])
    data[,10] <- clean_presentage(data[,10])
    data[,11] <- clean_presentage(data[,11])
    data[,13] <- clean_presentage(data[,13])
    data[,14] <- clean_presentage(data[,14])
    data[,1] <- countrycode(data[,2],origin = 'country.name' , destination = 'iso3c')
    
  }else{
    url <-paste("https://globalhealth5050.org/?_covid-data=countries&_vartype=deaths_pct&_country=",
                 country,"&_extype=csv",sep="")
    data <- read.csv2(url, sep=",")
    colnames(data) <- c("date", "total_covid_deaths", "male_covid_deaths","female_covid_deaths")
    data$date <- set_date_week(data$date)
    data$total_covid_deaths <- as.numeric.factor(data$total_covid_deaths)
    data$male_covid_deaths <- rounc(as.numeric.factor(data$male_covid_deaths) / 100 * 
                              data$total_covid_deaths)
    data$female_covid_deaths <- round(as.numeric.factor(data$female_covid_deaths) / 100 * 
                              data$total_covid_deaths)
  }
  return(data)
}




merge_globalheath_covid19dh <- function(country,data, verbose=T){
  if(missing(data)){
    data <- covid19globalhealth(country)
  }
  data$total_covid_deaths[data$total_covid_deaths == 0] <- NA
  covid_19 <- covid19(country, level = 1, verbose = verbose)
  df <- select(covid_19, date,confirmed,deaths, hosp, icu,tests, vaccines)
  df2 <- merge(df,data,by="date",all=T)
  
  diff <- sum(abs(ifelse(is.na(df2$deaths[!is.na(df2$total_covid_deaths)]),0,
                       df2$deaths[!is.na(df2$total_covid_deaths)]) - 
                    df2$total_covid_deaths[!is.na(df2$total_covid_deaths)]))
  if(verbose == T){
    cat("Difference in data is", diff," deaths!\n")
  }
  
  return(df2)
}


test_data <- function(data){
  total <- sum(as.numeric(data$total_covid_death),na.rm = T)
  male <- sum(as.numeric(data$male_covid_death),na.rm = T)
  female <- sum(as.numeric(data$female_covid_death),na.rm = T)
  nc <- sum(as.numeric(data$NC_covid_death),na.rm = T)
  cat("Latest date:", max(data$date),"\n")
  cat("Diff deaths:", total - (male + female + nc),
      "\nTotal deaths:", total, 
      "\nMale deaths:", male, 
      "\nFemale deaths:", female, 
      "\nNC deaths:", nc,"\n--------------\n")
}

```




# UK


Data given by https://www.ons.gov.uk/ 



```{r}

get_covid_uk <- function(level = 1){
  link_uk <- "https://www.ons.gov.uk/file?uri=/peoplepopulationandcommunity/birthsdeathsandmarriages/deaths/datasets/weeklyprovisionalfiguresondeathsregisteredinenglandandwales/2021/publishedweek052021.xlsx"
  GET(link_uk, write_disk(tf <- tempfile(fileext = ".xlsx")))
  UK <- read_excel(tf, 9)
  
  search_for_uk <- c("Week number","Persons 4",
                     "Deaths by region of usual residence 5", 
                     "Males 4", "Females 4")
  l <- list()
  find_rows <- function(data,column_nr, search_for){
    df <- data.frame(Rows = rep(NA,length(search_for)))
    rownames(df) <- search_for
    for(s in search_for){
      for(i in column_nr){
        if(s %in% unlist(data[,i])){
          df[s,1] <- which(s == unlist(data[,i]))
        }
      }
    }
    return(df)
  }
  rows <- find_rows(UK, c(1,2), search_for_uk)
  
  age_groups_uk <- c(UK$...2[11:30])
  age_matrix <- matrix(nrow = 20,ncol = 2)
  for(i in 1:length(age_groups_uk)){
    age <- strsplit(age_groups_uk[i],"-")[[1]]
    if(i == 1)
      age <- c(0,1)
     if(i == 20)
      age <- c(90,NA)
    
    age_matrix[i,] <- age
  }

  sum_by_group <- function(data,row,col){
    return(as.integer(colSums(data[row,col],na.rm = T)))
  }

  data <- UK[c(rows$Rows[1],rows$Rows[2]:rows$Rows[3]),]
  nc <- ncol(data)
  nage <- length(age_groups_uk) 
  if(level == 1 | level == 4){
    s <- 2
    nage <- nage + 1
    total_covid_deaths <-  sum_by_group(data,c(s:(s+nage)),c(3:(nc-1)))
    s <- s+nage + 1 
    male_covid_deaths <- sum_by_group(data,c(s:(s+nage)),c(3:(nc-1)))
    s <- s+nage + 1
    female_covid_deaths <- sum_by_group(data,c(s:(s+nage)),c(3:(nc-1)))
    
    date <- c(as.Date(paste(2020, 0:51, 5, sep="-"), "%Y-%U-%u"),
              as.Date(paste(2021, 0:(as.integer(data[1,nc-1])), 5, sep="-"), "%Y-%U-%u"))
    df <- data.frame(WeekNo = c(as.integer(data[1,3:(nc-1)])),
                     Year = c(rep(2020,53),rep(2021,as.integer(data[1,nc-1]))),
                     date = date,
                     total_covid_deaths = total_covid_deaths,
                     male_covid_deaths = male_covid_deaths,
                     female_covid_deaths = female_covid_deaths,
                     country = "UK",
                     Type = "Gender"
                     )
    l$level1 <- df
  }
  if(level == 2 | level == 4){
    
    rows2 <- find_rows(data,2,c("Persons 4",
                     "Males 4", "Females 4",
                     "Deaths by region of usual residence 5"))

    df <- data.frame(AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     Year = as.integer(), 
                     WeekNo = as.integer(), 
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    
    for(c in 3:(ncol(data)-1)){
      y <- 2020
      if(c > 55)
        y <- 2021
      
      df <- rbind(df,
                   data.frame(AgeGrp_min = age_matrix[,1], 
                   AgeGrp_max = age_matrix[,2], 
                   NUTS = "UK", 
                   Year = y, 
                   WeekNo = as.integer(data[1,c]), 
                   male_covid_death = unlist(data[(rows2$Rows[2]+2):(rows2$Rows[3]-1), c]), 
                   female_covid_death = unlist(data[(rows2$Rows[3]+2):(rows2$Rows[4]-1), c]), 
                   total_covid_death = unlist(data[(rows2$Rows[1]+2):(rows2$Rows[2]-1), c]), 
                   country = "UK", 
                   type = "AgeGender"
                  ))
      
    }
    l$level2 <- df
  }
  return(l)
}

```

```{r}
#UK1 <- get_covid_uk(level = 1)
UKl <- get_covid_uk(level = 4)
UK1 <- UKl$level1 
UK2 <- UKl$level2 
```


```{r}
test_data(UK1)
test_data(UK2)
```



```{r}
write.csv2(UK1, "covid-data/COVID-19-UK-level-1.csv")
write.csv2(UK2, "covid-data/COVID-19-UK-level-2.csv")

```




# Germany



```{r}
get_covid_germany <- function(level = 1){
  cat("Warning Large file! about 5 min to load.\n")
  g_link <- "https://opendata.arcgis.com/datasets/dd4580c810204019a7b8eb3e0b329dd6_0.csv"
  ge2 <- read.csv2(g_link, sep=",")
  colnames(ge2) <- c("stateID", "state_id", "state", "district", 
                         "age_group", "gender", "No_cases", 
                         "No_death", "date_hdp_aware", "county_id", 
                         "data_status", "new_case","new_death", 
                         "ref_date","new_recovery", "No_recovery","onset_of_disease",
                         "age_group2"
                         )
  new_case_info <- data.frame(nr=c(0,1,-1,NA),info=c("Case is included in the publication for the 
                                          current day and in the one for the previous day",
                                          "Case is only included in the current publication",
                                          "Case is only included in the previous day's publication",
                                          "This results in: number of cases in the current publication 
                                          as a sum (number of cases), if new case in (0.1); Delta on 
                                          the previous day as the sum (number of cases) if new case 
                                          in (-1.1)"))
  new_death_info <- data.frame(nr=c(0,1,-1,-9,NA),info=c("0:The case in the publication is one death for the 
                                                current day and one for the previous day",
                                                "1: The case is a death in the current publication,
                                                but not in the previous day's publication",
                                                "-1: all is not a death in the current publication,
                                                 however, it was a death in the previous day's publication",
                                                "-9: The case is neither in the current publication nor in that
                                                of the previous day a death",
                                                "number of deaths in the current publication as a total 
                                                (number of deaths) if new death in (0.1); Delta on the 
                                                previous day as total (number of deaths) if new deaths 
                                                in (-1.1)"))
  
  ge2_death <- ge2[ge2$No_death >0,] # Use only confirmed data 
  
  f <- function(i){
    d <- strsplit(i,",")[[1]][1]
    return(strsplit(as.character(d), " ")[[1]][1])
  }
  # Get date in new format
  ge2_death$date <- unlist(lapply(ge2_death$date_hdp_aware, f))
  # Translate gender
  ge2_death$gender <- ifelse(ge2_death$gender == "M", "male", ge2_death$gender)
  ge2_death$gender <- ifelse(ge2_death$gender == "W", "female", ge2_death$gender)
  ge2_death$gender <- ifelse(ge2_death$gender == "unbekannt", "NC", ge2_death$gender)
  l <- list()
  if(level== 1 | level == 4){
    date <- unique(ge2_death$date)
    sex <- unique(ge2_death$gender)
    df <- matrix(NA,ncol = 7, nrow = length(date))
    i <- 1
    for(d in date){
      dfm <- sum(ge2_death$No_death[which(ge2_death$gender == "male" & ge2_death$date == d)],na.rm = T)
      dff <- sum(ge2_death$No_death[which(ge2_death$gender == "female" & ge2_death$date == d)],na.rm = T)
      dfnc <- sum(ge2_death$No_death[which(ge2_death$gender == "NC" & ge2_death$date == d)],na.rm = T)
      dft <- dfnc + dff + dfm
      w <- strftime(d, format = "%V")
      y <- strsplit(d,"/")[[1]][1]
      df[i,] <- c(d,y,w, dft,dfm, dff, dfnc)
      i <- i +1
      
    }
    
    
    df <- data.frame(df)
    colnames(df) <- c("date","Year","WeekNo", "total_covid_death", "male_covid_death", 
                      "female_covid_death","NC_covid_death")
    df$country = "Germany"
    df$Type = "Gender"
                     

  }
  l$level1 = df
  if(level == 2 | level == 4){
    age_groups <- unique(ge2_death$age_group)
    age_matrix <- matrix(nrow = 7,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i],"-")[[1]]
      age[1] <- as.numeric(strsplit(age[1],"A")[[1]][2])
      age[2] <- as.numeric(strsplit(age[2],"A")[[1]][2])
      if(i == 2)
        age <- c(80,NA)
       if(i == 6)
        age <- c(NA,NA)
      
      age_matrix[i,] <- age
    }
    df <- data.frame(AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(),
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    
    for(d in date){
      a_it <- 1
       for(a in age_groups){
        df2 <- ge2_death[ge2_death$date == d & ge2_death$age_group == a,]
        w <- strftime(d, format = "%V")
        y <- strsplit(d,"/")[[1]][1]
        
        df <- rbind(df,
                     data.frame(AgeGrp_min = age_matrix[,1][a_it], 
                     AgeGrp_max = age_matrix[,2][a_it], 
                     NUTS = "Germany", 
                     date = d, 
                     Year = y,
                     WeekNo = w,
                     male_covid_death = sum(df2$No_death[df2$gender == "male"],na.rm = T), 
                     female_covid_death = sum(df2$No_death[df2$gender == "female"],na.rm = T), 
                     NC_covid_death = sum(df2$No_death[df2$gender == "NC"],na.rm = T),
                     total_covid_death = sum(df2$No_death,na.rm = T), 
                     country = "Germany", 
                     type = "AgeGender"
                    ))
        a_it <- a_it + 1
        
       }
    }
    l$level2 <- df
  }
  return(l)

}

```


```{r}
#germany1 <- get_covid_germany(level = 1)
#germany2 <- get_covid_germany(level = 2)

```

```{r}
germanyl <- get_covid_germany(level = 4)
germany1 <- germanyl$level1
germany2 <- germanyl$level2
```

```{r}
#sum(as.numeric(germany1$total_covid_death),na.rm = T)

test_data(germany1)
test_data(germany2)
```


```{r}

write.csv2(germany1, "covid-data/COVID-19-GERMANY-level-1.csv")
write.csv2(germany2, "covid-data/COVID-19-GERMANY-level-2.csv")

```




# Sweden



```{r}
# Data from Folkhäslomyndigheten 
# Only level 1 is possible at the moment. 
library(readxl)
get_covid_sweden <- function(level =  1){
  swe_dead <- read_excel("swe/dead_gender.xlsx")
  colnames(swe_dead) <- c("date", "dead_male", "dead_female")
  l <- list()
  if(level== 1 | level == 4){
    date <- as.Date(swe_dead$date)
    df <- matrix(NA,ncol = 7, nrow = length(date))
    for(r in 1:nrow(swe_dead)){
      dfm <- sum(swe_dead$dead_male[r], na.rm = T)
      dff <- sum(swe_dead$dead_female[r],na.rm = T)
      dfnc <- 0
      dft <- dfnc + dff + dfm
      w <- strftime(as.character(date[r]), format = "%V")
      y <- strsplit(as.character(date[r]),"-")[[1]][1]
      df[r,] <- c(as.character(date[r]),y,w, dft,dfm, dff, dfnc)
    }
    
    df <- data.frame(df)
    colnames(df) <- c("date","Year","WeekNo", "total_covid_death", "male_covid_death", 
                      "female_covid_death","NC_covid_death")
    df$country = "Sweden"
    df$Type = "Gender"
    l$level1 <- df                 
  }
  return(l)
}

#sweden <- merge_globalheath_covid19dh(country = "Sweden")

```






```{r}
swedenl <- get_covid_sweden(level = 4)
sweden1 <- swedenl$level1
test_data(sweden1)
```

```{r}
write.csv2(sweden1, "covid-data/COVID-19-SWEDEN-level-1.csv")

```



# Denmark


```{r}
#denmark<- merge_globalheath_covid19dh(country = "Denmark")

```



# Spain




```{r}

get_covid_spain <- function(level=1){
  spain_link <- "https://cnecovid.isciii.es/covid19/resources/casos_hosp_uci_def_sexo_edad_provres.csv"
  spain <- read.csv2(spain_link,sep=",")
  # Translation 
  colnames(spain) <- c("iso_province", "sex", "age_group","date",
                     "nr_cases","nr_hospital","nr_icu","deaths")
  spain$sex <- ifelse(spain$sex == "H", "male",spain$sex)
  spain$sex <- ifelse(spain$sex == "M", "female",spain$sex)
  spain$sex <- ifelse(spain$sex == "NC", "NC",spain$sex)
  l <- list()
  date <- unique(spain$date)
  sex <- unique(spain$sex)
  if(level== 1 | level == 4){
    date <- unique(spain$date)
    sex <- unique(spain$sex)
    df <- matrix(NA,ncol = 7, nrow = length(date))
    i <- 1
    for(d in date){
      dfm <- sum(spain$deaths[which(spain$sex == "male" & spain$date == d)])
      dff <- sum(spain$deaths[which(spain$sex == "female" & spain$date == d)])
      dfnc <- sum(spain$deaths[which(spain$sex == "NC" & spain$date == d)])
      dft <- dfnc + dff + dfm
      w <- strftime(d, format = "%V")
      y <- strsplit(d,"-")[[1]][1]
      df[i,] <- c(d,y,w, dft,dfm, dff, dfnc)
      i <- i +1
      
    }
    
    
    df <- data.frame(df)
    colnames(df) <- c("date","Year","WeekNo", "total_covid_death", "male_covid_death", 
                      "female_covid_death","NC_covid_death")
    df$country = "Spain"
    df$Type = "Gender"
    l$level1 <- df                

  }
  if(level == 2 | level == 4){
    age_groups <- unique(spain$age_group)
    age_matrix <- matrix(nrow = 10,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i],"-")[[1]]
      if(i == 9)
        age <- c(80,NA)
       if(i == 10)
        age <- c(NA,NA)
      
      age_matrix[i,] <- age
    }
    df <- data.frame(AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(),
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    
    for(d in date){
      a_it <- 1
       for(a in age_groups){
        df2 <- spain[spain$date == d & spain$age_group == a,]
        w <- strftime(d, format = "%V")
        y <- strsplit(d,"-")[[1]][1]
        
        df <- rbind(df,
                     data.frame(AgeGrp_min = age_matrix[,1][a_it], 
                     AgeGrp_max = age_matrix[,2][a_it], 
                     NUTS = "Spain", 
                     date = d, 
                     Year = y,
                     WeekNo = w,
                     male_covid_death = sum(df2$deaths[df2$sex == "male"],na.rm = T), 
                     female_covid_death = sum(df2$deaths[df2$sex == "female"],na.rm = T), 
                     NC_covid_death = sum(df2$deaths[df2$sex == "NC"],na.rm = T),
                     total_covid_death = sum(df2$deaths,na.rm = T), 
                     country = "Spain", 
                     type = "AgeGender"
                    ))
        a_it <- a_it + 1
        
       }
    }
    l$level2 <- df
  }
  if(level == 3 | level == 4){
    region <- unique(spain$iso_province)
    age_groups <- unique(spain$age_group)
    age_matrix <- matrix(nrow = 10,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i],"-")[[1]]
      if(i == 9)
        age <- c(80,NA)
       if(i == 10)
        age <- c(NA,NA)
      
      age_matrix[i,] <- age
    }
    df <- data.frame(region = as.character(),
                     AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(),
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    for(r in region){
      for(d in date){
        a_it <- 1
         for(a in age_groups){
           
          df2 <- spain[spain$date == d & spain$age_group == a & spain$iso_province == r,]
          w <- strftime(d, format = "%V")
          y <- strsplit(d,"-")[[1]][1]
          
          df <- rbind(df,
                       data.frame(region = r,
                         AgeGrp_min = age_matrix[,1][a_it], 
                       AgeGrp_max = age_matrix[,2][a_it], 
                       NUTS = "Spain", 
                       date = d, 
                       Year = y,
                       WeekNo = w,
                       male_covid_death = sum(df2$deaths[df2$sex == "male"],na.rm = T), 
                       female_covid_death = sum(df2$deaths[df2$sex == "female"],na.rm=T), 
                       NC_covid_death = sum(df2$deaths[df2$sex == "NC"], na.rm = T),
                       total_covid_death = sum(df2$deaths,na.rm = T), 
                       country = "Spain", 
                       type = "RegionAgeGender"
                      ))
          a_it <- a_it + 1
          
         }
      }
      #cat("Region:",r,"done.\n")
    }
    l$level3 <- df
  }
  
  return(l)
}
```

```{r}
table(spain$iso_province)
u <- unique(spain$iso_province)
(u)
```
```{r}

```



```{r}
#spain1 <- get_covid_spain(level = 1)
#spain2 <- get_covid_spain(level = 2)
spainl <- get_covid_spain(level = 4)
spain1 <- spainl$level1
spain2 <- spainl$level2
spain3 <- spainl$level3
```

```{r}
test_data(spain1)
test_data(spain2)
test_data(spain3)
```


```{r}
write.csv2(spain1, "covid-data/COVID-19-SPAIN-level-1.csv")
write.csv2(spain2, "covid-data/COVID-19-SPAIN-level-2.csv")
write.csv2(spain3, "covid-data/COVID-19-SPAIN-level-3.csv")

```





# Italy

```{r}


#italy <- merge_globalheath_covid19dh(country = "Italy")

```


# Belgium

```{r}
#belgium <- merge_globalheath_covid19dh(country = "Belgium")

```



```{r}
get_covid_belgium <- function(level = 1){
  belgium_link <- "https://epistat.sciensano.be/Data/COVID19BE_MORT.csv"
  belgium <- read.csv2(belgium_link,sep=",")
  date <- unique(belgium$DATE)
  sex <- unique(belgium$SEX)
  l <- list()
  if(level== 1 | level == 4){
    
    df <- matrix(NA,ncol = 7, nrow = length(date))
    i <- 1
    for(d in date){
      dfm <- sum(belgium$DEATHS[which(belgium$SEX == "M" & belgium$DATE == d)],na.rm = T)
      dff <- sum(belgium$DEATHS[which(belgium$SEX == "F" & belgium$DATE == d)],na.rm = T)
      dfnc <- sum(belgium$DEATHS[which(is.na(belgium$SEX) & belgium$DATE == d)],na.rm = T)
      dft <- dfnc + dff + dfm
      w <- strftime(d, format = "%V")
      y <- strsplit(d,"-")[[1]][1]
      df[i,] <- c(d,y,w, dft,dfm, dff, dfnc)
      i <- i +1
    }
    
    df <- data.frame(df)
    colnames(df) <- c("date","Year","WeekNo", "total_covid_death", "male_covid_death", 
                      "female_covid_death","NC_covid_death")
    df$country = "Belgium"
    df$Type = "Gender"
    l$level1 <- df                 
  }
  if(level == 2 | level == 4){
    age_groups <- unique(belgium$AGEGROUP)
    age_matrix <- matrix(nrow = 7,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i],"-")[[1]]
      if(i == 1)
        age <- c(80,NA)
       if(i == 7)
        age <- c(NA,NA)
      
      age_matrix[i,] <- age
    }
    df <- data.frame(AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(), 
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    
    for(d in date){
      a_it <- 1
       for(a in age_groups){
        df2 <- belgium[belgium$DATE == d & belgium$AGEGROUP == a,]
        w <- strftime(d, format = "%V")
        y <- strsplit(d,"-")[[1]][1]
        
        df <- rbind(df,
                     data.frame(AgeGrp_min = age_matrix[,1][a_it], 
                     AgeGrp_max = age_matrix[,2][a_it], 
                     NUTS = "Belgium", 
                     date = d,
                     Year = y,
                     WeekNo = w,
                     male_covid_death = sum(df2$DEATHS[df2$SEX == "M"],na.rm = T), 
                     female_covid_death = sum(df2$DEATHS[df2$SEX == "F"],na.rm = T), 
                     NC_covid_death = sum(df2$DEATHS[is.na(df2$SEX)],na.rm = T),
                     total_covid_death = sum(df2$DEATHS,na.rm = T), 
                     country = "Belgium", 
                     type = "AgeGender"
                    ))
        a_it <- a_it + 1
        
       }
    }
    l$level2 <- df
  }
   if(level == 3 | level == 4){
    age_groups <- unique(belgium$AGEGROUP)
    age_matrix <- matrix(nrow = 7,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i],"-")[[1]]
      if(i == 1)
        age <- c(80,NA)
       if(i == 7)
        age <- c(NA,NA)
      
      age_matrix[i,] <- age
    }
    region <- unique(belgium$REGION)
    df <- data.frame(region = as.character(),
                     AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(), 
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    for(r in region){
      
      for(d in date){
        a_it <- 1
         for(a in age_groups){
          df2 <- belgium[belgium$DATE == d & belgium$AGEGROUP == a & belgium$REGION == r,]
          w <- strftime(d, format = "%V")
          y <- strsplit(d,"-")[[1]][1]
          
          df <- rbind(df,
                       data.frame(region = r,
                         AgeGrp_min = age_matrix[,1][a_it], 
                       AgeGrp_max = age_matrix[,2][a_it], 
                       NUTS = "Belgium", 
                       date = d,
                       Year = y,
                       WeekNo = w,
                       male_covid_death = sum(df2$DEATHS[df2$SEX == "M"],na.rm = T), 
                       female_covid_death = sum(df2$DEATHS[df2$SEX == "F"],na.rm = T), 
                       NC_covid_death = sum(df2$DEATHS[is.na(df2$SEX)],na.rm = T),
                       total_covid_death = sum(df2$DEATHS,na.rm = T), 
                       country = "Belgium", 
                       type = "AgeGender"
                      ))
          a_it <- a_it + 1
          
         }
      }
    }
    l$level3 <- df
  }
  return(l)
}
```

```{r}
#belgium1 <- get_covid_belgium(level = 1)
#belgium2 <- get_covid_belgium(level = 2)

```

```{r}
belgiuml <- get_covid_belgium(level = 4)
belgium1 <- belgiuml$level1
belgium2 <- belgiuml$level2
belgium3 <- belgiuml$level3
```

```{r}
test_data(belgium1)
test_data(belgium2)
test_data(belgium3)

```





```{r}
write.csv2(belgium1, "covid-data/COVID-19-BELGIUM-level-1.csv")
write.csv2(belgium2, "covid-data/COVID-19-BELGIUM-level-2.csv")
write.csv2(belgium3, "covid-data/COVID-19-BELGIUM-level-3.csv")

```

# Switzerland 










```{r}
get_covid_switzerland <- function(level = 1){
  # zip file that has to be open 
  cat("Warning! Big file 120 mb about 10 min runtime.\n")
  swi_link <- "https://www.bag.admin.ch/dam/bag/en/dokumente/mt/k-und-i/aktuelle-ausbrueche-pandemien/2019-nCoV/covid-19-basisdaten-fallzahlen.csv.download.csv/Data%20on%20laboratory%20findings%20and%20deaths.csv"

  swi <- read.csv2(swi_link, sep=";")
  colnames(swi) <- c("X", "col_date", "case_date", "Kanton", "age", "sex",
                     "gender","sex2", "nr_confirmed_tests","death_date","nr_deaths")
  swi$gender <- ifelse(swi$gender == "Weiblich", "female",swi$gender)
  swi$gender <- ifelse(swi$gender == "Männlich", "male",swi$gender)
  swi$gender <- ifelse(swi$gender == "Unbekannt", "NC",swi$gender)
  l <- list()
  # deaths
  swi2 <- swi[which(swi$nr_deaths > 0),]
  date <- unique(swi2$death_date)
  sex <- unique(swi2$gender)
  if(level == 1 | level == 4){
    
    df <- matrix(NA,ncol = 7, nrow = length(date))
    i <- 1
    for(d in date){
      df2 <- swi2[which(swi2$death_date == d),]
      dfm <- nrow(df2[which(df2$gender == "male"),])
      dff <- nrow(df2[which(df2$gender == "female"),])
      dfnc <- nrow(df2[which(df2$gender == "unknown"),])
      w <- strftime(d, format = "%V")
      y <- strsplit(d,"-")[[1]][1]
      dft <- dfnc + dff + dfm
      df[i,] <- c(d, y, w, dft, dfm, dff, dfnc)
      i <- i +1
    }
    
    df <- data.frame(df)
    colnames(df) <- c("date","Year","WeekNo", "total_covid_death", "male_covid_death", 
                      "female_covid_death","NC_covid_death")
    df$country = "Switzerland"
    df$Type = "Gender"
    l$level1 <- df               
  }
  if(level == 2 | level == 4){
    
    age_groups <- unique(swi2$age)
    age_matrix <- matrix(nrow = 8,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i]," - ")[[1]]
      if(i == 1)
        age <- c(80,NA)
      
      age_matrix[i,] <- age
    }
    
    df <- data.frame(AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(), 
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    
    for(d in date){
      a_it <- 1
       for(a in age_groups){
        df2 <- swi2[swi2$death_date == d & swi2$age == a,]
        w <- strftime(d, format = "%V")
        y <- strsplit(as.character(d),"-")[[1]][1]

        df <- rbind(df,
                     data.frame(AgeGrp_min = age_matrix[,1][a_it], 
                     AgeGrp_max = age_matrix[,2][a_it], 
                     NUTS = "Switzerland", 
                     date = d,
                     Year = y,
                     WeekNo = w,
                     male_covid_death = nrow(df2[df2$gender == "male",]), 
                     female_covid_death = nrow(df2[df2$gender == "female",]), 
                     NC_covid_death = nrow(df2[df2$gender == "NC",]),
                     total_covid_death = nrow(df2), 
                     country = "Switzerland", 
                     type = "AgeGender"
                    ))
        a_it <- a_it + 1
        
       }
    }
    l$level2 <- df
  }
  if(level == 3 | level == 4){
    
    age_groups <- unique(swi2$age)
    age_matrix <- matrix(nrow = 8,ncol = 2)
    for(i in 1:length(age_groups)){
      age <- strsplit(age_groups[i]," - ")[[1]]
      if(i == 1)
        age <- c(80,NA)
      
      age_matrix[i,] <- age
    }
    region <- unique(swi2$Kanton)
    df <- data.frame(region = as.character(),
                     AgeGrp_min = as.numeric(), 
                     AgeGrp_max = as.numeric(), 
                     NUTS = as.character(), 
                     date = as.character(), 
                     Year = as.integer(),
                     WeekNo = as.integer(),
                     male_covid_death = as.integer(), 
                     female_covid_death = as.integer(), 
                     NC_covid_death = as.integer(),
                     total_covid_death = as.integer(), 
                     country = as.character(), 
                     type = as.character())
    for(r in region){
      for(d in date){
        a_it <- 1
         for(a in age_groups){
          df2 <- swi2[swi2$death_date == d & swi2$age == a & swi2$Kanton == r,]
          w <- strftime(d, format = "%V")
          y <- strsplit(as.character(d),"-")[[1]][1]
  
          df <- rbind(df,
                       data.frame(region = r, 
                                  AgeGrp_min = age_matrix[,1][a_it], 
                       AgeGrp_max = age_matrix[,2][a_it], 
                       NUTS = "Switzerland", 
                       date = d,
                       Year = y,
                       WeekNo = w,
                       male_covid_death = nrow(df2[df2$gender == "male",]), 
                       female_covid_death = nrow(df2[df2$gender == "female",]), 
                       NC_covid_death = nrow(df2[df2$gender == "NC",]),
                       total_covid_death = nrow(df2), 
                       country = "Switzerland", 
                       type = "AgeGender"
                      ))
          a_it <- a_it + 1
          
         }
      }
    }
    l$level3 <- df
  }
  return(l)
}
```


```{r}
#switzerland1 <- get_covid_switzerland(level = 1)
switzerlandl <- get_covid_switzerland(level = 4)
switzerland1 <- switzerlandl$level1
switzerland2 <- switzerlandl$level2
switzerland3 <- switzerlandl$level3

```

```{r}
test_data(switzerland1)
test_data(switzerland2)
test_data(switzerland3)

```



```{r}
write.csv2(switzerland1, "covid-data/COVID-19-SWITZERLAND-level-1.csv")
write.csv2(switzerland2, "covid-data/COVID-19-SWITZERLAND-level-2.csv")
write.csv2(switzerland3, "covid-data/COVID-19-SWITZERLAND-level-3.csv")

```



# sources

```{r}
sources <- data.frame(country = c("UK", "Sapin", "Belgium", "Switzerland","Sweden", 
                                  "Denmark", "Germany","Italy"), 
                      source = c("https://www.ons.gov.uk/",#UK
                                 "https://cnecovid.isciii.es/",#Spain 
                                 "https://epistat.sciensano.be/", # Belgium
                                 "https://www.bag.admin.ch/",# Switzerland
                                 "https://www.folkhalsomyndigheten.se/",# Sweden
                                 NA, # Denmark
                                 "https://opendata.arcgis.com/", #Germany
                                 NA # Italy
                                 ))
```


```{r}
write.csv2(sources,"covid-data/sources.csv")
```



# Other

Links to websites of statistical offices of each country: 
UK: https://www.ons.gov.uk 
Germany: https://www.destatis.de/EN/Home/_node.html 
Sweden: https://www.scb.se/en/ 
Denmark: https://www.dst.dk/en 
Spain: https://www.ine.es/en/index.htm 
Italy: https://www.istat.it/en/archivio/240106 
Belgium: https://statbel.fgov.be/en/covid-19-statbel-data 
Switzerland: https://www.bfs.admin.ch/bfs/en/home.html
Look also at the following data sources: 
https://globalhealth5050.org/the-sex-gender-and-covid-19-project/
https://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=demo_r_mweek3 
https://github.com/CSSEGISandData/COVID-19/blob/master/README.md 
https://coronavirus.data.gov.uk/details/download
https://www.bag.admin.ch/bag/en/home/krankheiten/ausbrueche-epidemien-pandemien/aktuelle-ausbrueche-epidemien/novel-cov/situation-schweiz-und-international.html














